\label{section:introduction}%

The minimum feedback arc set problem is a canonical NP-Complete problem given by
\citet{KarpNPComplete}. Worse still, \citet{kannthesis} showed that the problem
is APX-hard. Despite these results finding the minimum feedback arc set of a
directed graph is desirable for many domains: such as certain rank-choice voting
systems, tournament ranking systems \citet{tournamentsRfast}, and dependency graphs
in general.

Solutions to the minimum feedback arc set problem are commonly implemented in
widely used graph libraries yet all suffer from a distinct flaw. While each
implementation provides a solution, the implementations only do so without
allowing the user to inspect intermediate steps; which might contain useful
domain information. For example, the graph \autoref{fig:tournament-graph}
displays a directed graph which encodes a single win tournament system. Each
vertex is a player and each edge encodes a win over a contestant, for example we
see that player E beat contestant B. Observe that the
\autoref{fig:tournament-graph} contains cycles which implies that there is not a
linear ordering amongst the contestants of the tournament, and so any ranking of
the contestants would violate a win of one contestant over another. Removing the
minimum feedback arc set would remove the cycles, which yields a linear order in
the tournament that violates the fewest number of wins. In this example,
intermediate results are edges which compose the minimum feedback arc set, thus
if one had access to the intermediate results one might choose to rematch the
opponents rather than remove the win. Crucially, the result of the rematch may
change the final minimum feedback arc set. Such a procedure could therefore
increase the confidence in the results of the tournament.

To allow for \emph{inspectable incrementality} we propose a novel direction in
solving the minimum feedback arc set problem based on recent advances in
\ac{sat} and \ac{smt} solving. Our approach is to utilize an \ac{smt} solver to
detect cycles and minimize the weight of the feedback arc set. Incrementality in
this approach is given through use of an \emph{incremental} \ac{smt} solver and
generation of \emph{unsatisfiable cores}. A minimum unsatisfiable core is the
minimum set of clauses in a \ac{sat} or \ac{smt} formula which prevent a
\ac{sat} or \ac{smt} solver run from finding a satisfiable assignment. An
incremental solver provides the user the ability to add or remove constraints
and thereby direct the solver during runtime. Incrementality in our approach is
crucial as it allows the user decision points to interact with the solution
process. Thus, a user might observe a unsatisfiable core which corresponds to a
cycle and deliberately resample \emph{only} the edges in the discovered cycle.

Unfortunately, we find that incremental \ac{smt} for finding a minimum feedback
arc set suffers from significant issues which seem to be intractable. In
addition to this result we make the following contributions:
%
\begin{enumerate}
\item An identification of the most intractable problems for an incremental
  \ac{smt} encoding on the minimum feedback arc set problem.
  (\autoref{section:incremental})
\item An \ac{smt} encoding to find the minimum feedback arc set of an arbitrary
  directed and cyclic graph. (\autoref{section:gadgets})
\item An empirical evaluation of the \ac{smt} encoding.
  (\autoref{section:results-and-discussion})
\end{enumerate}



%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End: